External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

Now we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. For each subspace, we consider to use the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$. This dictionary has two parts: the external part $\mathbf{D}_{e}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is consisted of the first ($3p^2-r$) columns of the singular vector matrix $\mathbf{U}_{e}$ obtained from the external prior by Equ. (\ref{equ3}), and the internal part $\mathbf{D}_{i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs. The learning is performed under the sparse coding framework (along with which the denoising of real noisy image is simultaneously done) as follows:
\vspace{-2mm}
\begin{equation}\label{equ6}\vspace{-2mm}
\begin{split}
&\min_{\mathbf{D}_{i}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
\\
&
\text{s.t.}
\quad
\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Similar to the K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem \ref{equ4}. In fact, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}$ and for $t=0, 1, ..., T-1$, alternatively do:

\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparce coefficients via solving
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-2mm}
\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
\end{equation}
This problem has closed-form solution by $\mathbf{A}^{*}=T_{\lambda}(\mathbf{\hat{D}}^{T}\mathbf{Y})$, 
where $T_{\lambda}(\mathbf{A}) = \text{sgn}(\mathbf{A})\odot\max(\mathbf{A},\lambda)$ is a soft-thresholding function.

\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ8} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}:=
&
\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
\\
&
\text{s.t.}
\quad
\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The sparse coefficients $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively. According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ6}) 
%\begin{equation}
%\begin{split}
%\min_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
%&\|\mathbf{Y}-\mathbf{D}_{e}\mathbf{A}_{e}+\mathbf{D}_{i}\mathbf{A}_{i}\|_{F}^{2}
%\\
%&
%\text{s.t.}
%\quad
%\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
%\end{split}
%\end{equation}
has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}\mathbf{V}^{T}$, where $\mathbf{U}$ and $\mathbf{V}$ are
the orthogonal matrices obtained by the following SVD
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
=
\mathbf{U}\Sigma\mathbf{V}^{T}
\end{equation}
With these solutions, the final obtained dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ are orthogonal ictionary. This can be proved by the following equation
\vspace{-3mm}
\begin{equation}\label{equ10}\vspace{-3mm}
\mathbf{D}^{T}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{T}
\\
\mathbf{D}_{i}^{T}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

\subsection{Discussions}
Until now, we have divided the noisy PGs into multiple internal subspaces. Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs. The help are at least threefold. Firstly, through MAP in (\ref{equ3}), the external prior guides the noisy PGs to be clustered into the correct subspaces. If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise. Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs. It only needs to calculate the MAP probability via the equation (\ref{equ3}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}. Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive. This will bring better denoising performance than the methods only using the external information.

>>>>

Assume we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. For each subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$. This dictionary has two parts: the external part $\mathbf{D}_{e}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is consisted of the first ($3p^2-r$) columns of the singular vector matrix $\mathbf{U}_{e}$ obtained from the external prior by Equ. (\ref{equ3}), and the internal part $\mathbf{D}_{i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs. The learning is performed under the sparse coding framework (along with which the denoising of real noisy image is simultaneously done) as follows:
\vspace{-2mm}
\begin{equation}\label{equ6}\vspace{-2mm}
\begin{split}
&\min_{\mathbf{D}_{i}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
\\
&
\text{s.t.}
\quad
\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{e}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-1mm}
\mathbf{D}^{T}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{T}
\\
\mathbf{D}_{i}^{T}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ6}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{e}$ and for $t=0, 1, ..., T-1$, alternatively do:
\\
\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparse coefficients via solving
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
\end{equation}
Since dictionary $\mathbf{D}_{t}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problem (\ref{equ8}) has closed-form solution $\mathbf{A}^{(t)}=T_{\lambda}(\mathbf{D}_{t}^{T}\mathbf{Y})$, 
where $T_{\lambda}(\mathbf{\bullet
}) = \text{sgn}(\mathbf{\bullet
})\odot\max(\mathbf{\bullet
},\lambda)$ is soft-thresholding function and $\odot$ is element-wise product.
\\
\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ9} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}:=
&
\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
\\
&
\text{s.t.}
\quad
\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Here we ignore the index ($t$) for notation simplicity. The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively. According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9}) 
has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{T}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
\vspace{-2mm}
\begin{equation}\label{equ10}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{T}
\end{equation}

\subsection{Discussions}
Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs. The help are at least threefold. Firstly, through MAP in (\ref{equ3}), the external prior guides the noisy PGs to be clustered into the correct subspaces. If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise. Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs. It only needs to calculate the MAP probability via the equation (\ref{equ3}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}. Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive. This will bring better denoising performance than the methods only using the external information.
